decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw

\section{Wang-Wei-Zhu decomposition}
\label{sec:wwz}
The Wang-Wei-Zhu decomposition ...

>>>>

\section{Wang-Wei-Zhu decomposition}
\label{sec:wwz}
The Wang-Wei-Zhu decomposition builds upon the Leontief insight but uses, in addition, further valuable information
provided in ICIOS. More specifically, the Leontief decomposition traces the value added back to where it originates
but ICIOS also contain data on how the value added is subsequently used. This information is extracted by the
Wang-Wei-Zhu decomposition, which thereby allows a much more detailed look at the structures of international
production networks and the respective positions of countries and industries within them.
